---
title: "Json deck creation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

```{r, echo=FALSE}
library(tidyverse)
library(jsonlite)
library(readxl)
library(gsheet)
```

Import the url of the card back image:

```{r}
backimage_url <- "https://customcards.s3.us-east-2.amazonaws.com/card_back.jpg"
```

Import excel list of cards and their image urls. Images must be the direct links. E.g. must end in ".png"

Prompts the user to select the Excel file for import.

```{r}
## Import table from google sheets
cubecard_address <- "https://docs.google.com/spreadsheets/d/1e126rklurwrdjOKVxNV6DjIMTTkfNJ94niuSxmcYObM/edit#gid=397638921"
token_address <- "https://docs.google.com/spreadsheets/d/1e126rklurwrdjOKVxNV6DjIMTTkfNJ94niuSxmcYObM/edit#gid=990091517"
land_address <- "https://docs.google.com/spreadsheets/d/1e126rklurwrdjOKVxNV6DjIMTTkfNJ94niuSxmcYObM/edit#gid=2139880948"
```

Import the files

```{r}
## Prompt user to select which deck to import
import_option <- readline(prompt = "Select which deck to use:\n1=Cube cards\n2=Tokens\n3=Basic lands")
```


```{r}
## Import cube cards depending on which option was selected
option_cubecard <- 1
option_token <- 2
option_land <- 3

if (import_option == option_cubecard) {
  deck_import <- gsheet2tbl(cubecard_address)
} else if (import_option == option_token) {
  deck_import <- gsheet2tbl(token_address)
} else if (import_option == option_land) {
  deck_import <- gsheet2tbl(land_address)
} else {
  stop("Must pick options 1 thru 3")
}

## Filter out NA and select the relevant columns
deck_xl <- 
  deck_import %>% 
  filter(!is.na(card_title)) %>% 
  select(card_title, cascade_helper, url)
```

```{r}
## If the deck is the basic land deck, then replicate the cards so that there's enough cards to use.
if (import_option == option_land) {
  deck_xl <- 
    deck_xl %>% 
    slice(rep(1:n(), each = 20))
}
```

```{r}
deck_df <- 
  deck_xl %>% 
  transmute(card_name = paste0(card_title,
                               "\n",
                               cascade_helper),
            url = url) %>% 
  mutate(CardID = row_number() * 100,
         card_number = row_number())
```


Create the deck name.

```{r}
Name <- "DeckCustom"
```

Each card has a field called "Transform" that lists how the card is oriented and shaped. We'll use this as a field in the next ContainedObjects object.

```{r}
transform_obj <- list(posX = unbox(0),
                      posY = unbox(0),
                      posZ = unbox(0),
                      rotX = unbox(0),
                      rotY = unbox(180),
                      rotZ = unbox(180),
                      scaleX = unbox(1),
                      scaleY = unbox(1),
                      scaleZ = unbox(1)
                      )

## The entire deck also has a Transform object too, which is only different in the posY.
transform_obj_deck <- list(posX = unbox(0),
                           posY = unbox(1),
                           posZ = unbox(0),
                           rotX = unbox(0),
                           rotY = unbox(180),
                           rotZ = unbox(180),
                           scaleX = unbox(1),
                           scaleY = unbox(1),
                           scaleZ = unbox(1)
                           )
```

Create a tibble that has the cards.

```{r}
ContainedObjects <- 
  deck_df %>% 
  mutate(Name = "Card",
         Nickname = card_name,
         Transform = list(transform_obj)) %>% 
  select(CardID, Name, Nickname, Transform)
```

Create a vector of DeckIDs

```{r}
DeckIDs <- 
  ContainedObjects %>% 
  select(CardID) %>% 
  pull()
```

Create the CustomDeck object, which is a list of unique cards in the deck.

```{r}
CustomDeck_df <- 
  deck_df %>% 
  mutate(FaceURL = url,
         BackURL = backimage_url,
         NumHeight = 1,
         NumWidth = 1,
         BackIsHidden = TRUE) %>% 
  select(FaceURL, BackURL, NumHeight, NumWidth, BackIsHidden)


CustomDeck_transpose <- 
  CustomDeck_df %>% 
  transpose()

unboxeachitem <- function(x) {
  lapply(x, unbox)
}

CustomDeck <- 
  lapply(CustomDeck_transpose, unboxeachitem)

CustomDeck_names <- deck_df %>% 
  select(card_number) %>% 
  transmute(card_number = as.character(card_number)) %>% 
  pull()

names(CustomDeck) <- CustomDeck_names
```

Create the Transform object for the deck:

```{r}
Transform <- transform_obj_deck
```

Create the list that will eventually go into the ObjectStates array:

```{r}
ObjectStates_obj <- list(unbox(Name), ContainedObjects, DeckIDs, CustomDeck, Transform)
names(ObjectStates_obj) <- c("Name", "ContainedObjects", "DeckIDs", "CustomDeck", "Transform")
```

Create the named array:

```{r}
final_deck <- list(list(ObjectStates_obj))
names(final_deck) <- "ObjectStates"
```

Write the results

```{r}
date_id <- 
  format(Sys.time(),
         "%Y%m%d_%H%M%S")

write_json(final_deck,
           paste0("output/",
                  url_table_basename_noext,
                  "_",
                  date_id,
                  ".json")
           )
```




